### 2024-06-16 index.qmd
20240615 - CITES

In terms of my `R` and statistics background, I have published many [peer-reviewed publications](https://developmental-psychopathology.lab.uiowa.edu/publications) that employ advanced statistical methods, have published a [book on psychological assessment](https://www.routledge.com/9781032413068) that includes applied examples in `R`, and have published the [`petersenlab` `R` package](https://cran.r-project.org/web/packages/petersenlab/index.html) on the Comprehensive R Archive Network (CRAN).
I am also a co-author of the [`ffanalytics` `R` package](https://github.com/FantasyFootballAnalytics/ffanalytics) that provides free utilities for downloading fantasy football projections and additional fantasy-relevant data, and for calculating projected points given your league settings.

>>>>

In terms of my `R` and statistics background, I have published many [peer-reviewed publications](https://developmental-psychopathology.lab.uiowa.edu/publications) that employ advanced statistical methods, have published a [book on psychological assessment](https://www.routledge.com/9781032413068) [@Petersen2024a; @PetersenPrinciplesPsychAssessment] that includes applied examples in `R`, and have published the [`petersenlab` `R` package](https://cran.r-project.org/web/packages/petersenlab/index.html) [@R-petersenlab] on the Comprehensive R Archive Network (CRAN).
I am also a co-author of the [`ffanalytics` `R` package](https://github.com/FantasyFootballAnalytics/ffanalytics) that provides free utilities for downloading fantasy football projections and additional fantasy-relevant data, and for calculating projected points given your league settings.

### 2024-06-16 research-methods.qmd
20240615 - CITES

@@

@@

>>>>

Below, I provide brief discussions of various aspects of measurement reliability and validity.
For more information on these and other aspects of psychometrics, see @Petersen2024a and @PetersenPrinciplesPsychAssessment.

@@

For more information on these and other aspects of reliability, see <https://isaactpetersen.github.io/Principles-Psychological-Assessment/reliability.html> [@Petersen2024a; @PetersenPrinciplesPsychAssessment].

@@

For more information on these and other aspects of validity, see <https://isaactpetersen.github.io/Principles-Psychological-Assessment/validity.html> [@Petersen2024a; @PetersenPrinciplesPsychAssessment].
